Information dynamics in neuromorphic nanowire networks

### 2020-06-05 main.tex
format fixes

\subsection{\label{sec:level2} Centrality and Functionality}

@@

\subsection{Time-series analysis}

@@

\subsection{Pre activation task}

@@

\subsection{Graph Generalization}

@@

\subsection{\label{sec:level2} Simulation}
When connected to external voltage biases, nanowire networks behave like traditional electrical networks. Each component in the network obeys Kirchhoff's law. Hence the voltage distribution across the network can be obtained by solving (\cite{Dorfler2018}):

@@

\subsection{\label{sec:level2} Centrality}
Centrality \textbf{Put some reference here} is an important measure that helps understand the fundamental structures and connectivities of networks. Betweenness centrality of nodes and edges in networks can demonstrate .... Meanwhile, closeness centrality of nodes can be used to interpret the ..... \cite{Newman2010}.

@@

\subsection{\label{sec:level2} Communicability}
Communicability in a network represents .... \cite{Estrada2008}.

@@

\subsection{\label{sec:level2} Modularity}
Modularity is a network metric that ..... \textbf{talk about it here} \cite{Rubinov2009}.

@@

\subsection{\label{sec:level2} Information Dynamics}

@@

\subsection{Benchmark}

>>>>

\subsection*{Centrality and Functionality}

@@

\subsection*{Time-series analysis}

@@

\subsection*{Pre activation task}

@@

\subsection*{Graph Generalization}

@@

\subsection*{\label{sec:level2} Simulation}
When connected to external voltage biases, nanowire networks behave like traditional electrical networks. Each component in the network obeys Kirchhoff's law. Hence the voltage distribution across the network can be obtained by solving (\cite{Dorfler2018}):

@@

\subsection*{Centrality}
Centrality \textbf{Put some reference here} is an important measure that helps understand the fundamental structures and connectivities of networks. Betweenness centrality of nodes and edges in networks can demonstrate .... Meanwhile, closeness centrality of nodes can be used to interpret the ..... \cite{Newman2010}.

@@

\subsection*{Communicability}
Communicability in a network represents .... \cite{Estrada2008}.

@@

\subsection*{Modularity}
Modularity is a network metric that ..... \textbf{talk about it here} \cite{Rubinov2009}.

@@

\subsection*{Information Dynamics}

@@

\subsection*{Benchmark}
